Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-22 analysis/paper/paper.Rmd
Fixes another single/double quote around a score

However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than "1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).

>>>>

However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).
